### 2013-04-09 exam6/2.tex
add prob 3

@@

@@

\begin{solution}
\begin{verbatim}
//> 5pts all correct
//> Ok if they have another implementation if it's right

// in BST<X> interface
    // Add all elements of this BST to ls, in order.
    void addTo(ArrayList<X> ls);

>>>>

\begin{solution}
\begin{verbatim}
// 4 pts total
// 1 pt class structure
class Count implements Computation<Integer> {
    Integer i;
    Count() {
        this.i = 0;
    }

// 2 pts for run
    public Integer run() {
        Integer j = this.i;
        this.i = i+1;
        return j;
    }      
}
// 1 pt for tests
\end{verbatim}
\end{solution}

@@

\begin{solution}
\newpage
\begin{verbatim}
// 2 pt structure (including purpose etc)
class Thunk<X> implements Computation<X> {
    Delay<X> s;
    Thunk(Computation<X> c) {
        this.s = new Frozen<X>(c);
    }
// 2 pts 
    public X run() {
        this.s = this.s.force();
        return this.s.val();
    }
}
\end{verbatim}
\newpage
\begin{verbatim}
// 8 pts for the code in general, may have different design
interface Delay<X> {
    Delay<X> force();
    X val();
}
class Frozen<X> implements Delay<X> {
    Computation<X> c;
    Frozen(Computation<X> c) {
        this.c = c;
    }
    public Delay<X> force() {
        return new Thaw<X>(this.c.run());
    }
    public X val() {
        return null;
    }
}
class Thaw<X> implements Delay<X> {
    X x;
    Thaw(X x) {
        this.x = x;
    }
    public Delay<X> force() {
        return this;
    }
    public X val() {
        return this.x;
    }
}
\end{verbatim}
\newpage
\begin{verbatim}
// 2 pts tests
class Examples {
    void testThunk(Tester t) {
        Computation<Integer> count = new Count();
        t.checkExpect(count.run(), 0);
        t.checkExpect(count.run(), 1);
        t.checkExpect(count.run(), 2);
        t.checkExpect(count.run(), 3);
        Computation<Integer> thunk = new Thunk<Integer>(new Count());
        t.checkExpect(thunk.run(), 0);
        t.checkExpect(thunk.run(), 0);
    }

}
\end{verbatim}
\end{solution}

@@

\begin{solution}
\begin{verbatim}
// in BST<X> interface
    // Add all elements of this BST to ls, in order.
    void addTo(ArrayList<X> ls);
